---
title: "Graphic description"
description: |
  Description of a graph representing the evolution of the skeletal mass according to the origin of the sea urchins.
author:
  - name: Anne-Charlotte Vranckx
    url:
      https://github.com/AnneCharlotteVranckx: {https://github.com/AnneCharlotteVranckx}::
date: "`r Sys.Date()`"
preview: ../../images/urchin.jpg
categories:
  - "Data Sciences I"
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
SciViews::R
```

# Import and data description

```{r importation}
urchin <- data.io::read("urchin_bio", package = "data.io")
```

These data contain 19 variable measurements on *Paracentrotus lividus Larmarck (1816)*. This animal is a sea urchin. Individuals come from fishery (Brittany, France) and from a sea urchins farm in Normandy (France). These data used in this study come from Professor Philippe Grosjean's research on the growth of these sea urchins.


# Creation of the graphic

```{r}
chart(data = urchin, origin ~ skeleton %fill=% origin) +
  ggridges::geom_density_ridges(na.rm = TRUE) +
  ggtitle("Evolution of the mass of the skeleton (g) as a function of origin") +
  theme(legend.position="bottom") +
  theme(legend.background = element_rect(fill="white", size = 1, linetype="solid", color="#F0DBF0")) +
  scale_fill_manual(values = c("#F0DBF0", "#ECC9EC", "purple"))
```

# Analysis

We observe that sea urchins in the wild and farmed sea urchins have masses that are quite similar. The peak mass is the same in both cases: +/- 3g. We cannot see any considerable difference except that the sea urchins in the wild are more numerous to have a mass between 3 and 20g than farmed urchins.

